Conjure: Summoning Proxies from Unused Address Space

### 2019-09-25 paper/paper.tex
bib fixes and client github footnote

In this paper, we present \textbf{\scheme}, a Refraction
Networking protocol that overcomes these challenges while retaining
TapDance's ISP-friendly deployment requirements.
Our key innovation is an architecture that avoids
having to actively participate in client-to-decoy connections.

>>>>

In this paper, we present \textbf{\scheme}, a Refraction
Networking protocol that overcomes these challenges while retaining
TapDance's ISP-friendly deployment requirements~\footnote{
We have released the open source implementation of the Conjure client at 
\url{https://github.com/refraction-networking/gotapdance/tree/dark-decoy}.}.
Our key innovation is an architecture that avoids
having to actively participate in client-to-decoy connections.
